О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
The exact value of coefficient in the main estimate
Uniform linear bound

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c$ (TODO: the exact constant) in Theorem~\ref{thm:main_estimate},
using the combined approach with the Point Packing in a Square problem
(we notice that such an approach is different from Solymosi's one);
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.

@@

\begin{theorem}
	\label{thm:main_estimate}
	If $n\geq 4$, then $d(2,n) \geq \gamma (n - 2)$,
	where
	\begin{equation}
		\gamma = ... < \frac{3^{1/4}}{2^{3/2}}
	\end{equation}
	TODO!
\end{theorem}

@@

>>>>

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c = 5/11$ in Theorem~\ref{thm:main_estimate},
using the combined approach with the Point Packing in a Square problem
(we notice that such an approach is different from Solymosi's one);
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.

@@

\begin{theorem}
	\label{thm:main_estimate}
	If $n\geq 4$, then $d(2,n) \geq \gamma (n - 2)$,
	where
	\begin{multline}
		\frac{3^{1/4}}{2^{3/2}} >
		\gamma = \frac{\sqrt{16 {{\left( \sqrt{\frac{2}{\sqrt{3}}+\frac{1}{21490}}+\frac{1}{\sqrt{21490}}\right) }^{2}}+\frac{14791716}{{{\left( 2593 \sqrt{647}-5823\right) }^{2}}}}-\frac{3846}{2593 \sqrt{647}-5823}}{8 {{\left( \sqrt{\frac{2}{\sqrt{3}}+\frac{1}{21490}}+\frac{1}{\sqrt{21490}}\right) }^{2}}}
		>\\
		> 0.45557
		> \frac{5}{11}
	\end{multline}
\end{theorem}

@@

\begin{corollary}
	If $n\geq 4$, then $d(2,n) > \frac{5}{11} n$.
\end{corollary}

\begin{proof}
	For $4 \leq n \leq 21491$, the claim follows from Observation~\ref{obs:4_leq_n_leq_21491} immediately.
	For $n > 21491$, the inequality $0.45557(n-2) > \frac{5}{11}n$ holds.
\end{proof}
